---
title: "Multilevel Models - Combined Tables"
author:
  - Technical assistant
date: "`r Sys.Date()`"
format:
  docx:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
---

```{r packages and data}
pacman::p_load(
  tidyverse,
  haven,
  tidylog,
  huxtable,
  broom.mixed,
  glue,
  ggeffects
)

load("../../../output/models/main/results_mm_z.RData")
# load("output/models/main/results_mm_z.RData")

load("../../../output/models/main/results_mm_z_nse_cat.RData")
# load("output/models/main/results_mm_z_nse_cat.RData")

load("../../../output/models/main/results_mm_z_sin_stgo.RData")
# load("output/models/main/results_mm_z_sin_stgo.RData")

source("../../../analysis/helpers/labels.R")
# source("analysis/helpers/labels.R")

model_labels <- c("Null", "Individual", "Contextual", "Full", "Interaction")

# Replicar aproximación normal de texreg (t tratado como z)
tidy.lmerMod <- function(x, effects = "fixed", ...) {
  out <- broom.mixed:::tidy.merMod(x, effects = effects, ...)
  if ("statistic" %in% names(out)) {
    out$p.value <- 2 * pnorm(-abs(out$statistic))
  }
  out
}
```

```{r}
# Wrapper para modelos continuos (NSE continuo)
tab_mm <- function(model_list) {
  huxtable::huxreg(
    setNames(model_list, model_labels),
    coefs = setNames(names(coef_labels), coef_labels),
    stars = c(`*` = 0.05, `**` = 0.01, `***` = 0.001),
    bold_signif = 0.05,
    number_format = "%.2f"
  ) |> huxtable::set_font_size(9)
}

# Wrapper para modelos con NSE categórico
tab_mm_cat <- function(model_list) {
  huxtable::huxreg(
    setNames(model_list, model_labels),
    coefs = setNames(names(coef_labels_nse_cat), coef_labels_nse_cat),
    stars = c(`*` = 0.05, `**` = 0.01, `***` = 0.001),
    bold_signif = 0.05,
    number_format = "%.2f"
  ) |> huxtable::set_font_size(9)
}
```

# NSE Continuous

## ELSOC 2016

### Identification

```{r}
tab_mm(results_mm_z$elsoc_2016$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z$elsoc_2016$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z$elsoc_2016$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z$elsoc_2016$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z$elsoc_2016$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z$elsoc_2016$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z$elsoc_2016$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z$elsoc_2016$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z$elsoc_2016$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z$elsoc_2016$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z$elsoc_2016$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z$elsoc_2016$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z$elsoc_2016$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z$elsoc_2016$z_justif_violence)
```

## ELSOC 2019

### Identification

```{r}
tab_mm(results_mm_z$elsoc_2019$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z$elsoc_2019$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z$elsoc_2019$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z$elsoc_2019$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z$elsoc_2019$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z$elsoc_2019$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z$elsoc_2019$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z$elsoc_2019$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z$elsoc_2019$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z$elsoc_2019$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z$elsoc_2019$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z$elsoc_2019$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z$elsoc_2019$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z$elsoc_2019$z_justif_violence)
```

## ELSOC 2022

### Identification

```{r}
tab_mm(results_mm_z$elsoc_2022$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z$elsoc_2022$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z$elsoc_2022$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z$elsoc_2022$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z$elsoc_2022$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z$elsoc_2022$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z$elsoc_2022$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z$elsoc_2022$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z$elsoc_2022$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z$elsoc_2022$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z$elsoc_2022$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z$elsoc_2022$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z$elsoc_2022$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z$elsoc_2022$z_justif_violence)
```

# NSE Categorical

## ELSOC 2016

### Identification

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_identification)
```

### Friends

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_friends)
```

### Generalized trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2016$z_justif_violence)
```

## ELSOC 2019

### Identification

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_identification)
```

### Friends

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_friends)
```

### Generalized trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2019$z_justif_violence)
```

## ELSOC 2022

### Identification

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_identification)
```

### Friends

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_friends)
```

### Generalized trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm_cat(results_mm_z_nse_cat$elsoc_2022$z_justif_violence)
```

# NSE Continuous - Sin Santiago

## ELSOC 2016

### Identification

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2016$z_justif_violence)
```

## ELSOC 2019

### Identification

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2019$z_justif_violence)
```

## ELSOC 2022

### Identification

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_identification)
```

### Friends

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_friends)
```

### Generalized trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_gen_trust)
```

### Trust in minorities

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_trust_minorities)
```

### Institutional trust

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_trust_inst)
```

### Interest in politics

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_interest_pol)
```

### Satisfaction with democracy

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_satisf_demo)
```

### Conventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_conv_particip)
```

### Unconventional participation

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_unconv_particip)
```

### Egalitarianism

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_egalitarianism)
```

### Altruistic behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_altruistic)
```

### Prosocial behavior

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_prosoc_behave)
```

### Democracy support

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_democracy_support)
```

### Injustification of violence

```{r}
tab_mm(results_mm_z_sin_stgo$elsoc_2022$z_justif_violence)
```
